PANCHANGE_analysis

### 2020-08-25 PANCHANGE_analysis.Rmd
ethnicity and gender collapsing

@@

## GAD
```{r}
dat.gad <- dat.raw %>%
  drop_na()
  filter(
    (data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data")
  )

@@

# Positive covid test results
```{r}

@@

# COVID
## Recode variable
```{r gad covid test positive double}
dat <- dat %>%
  mutate(gad.covid_test_positive_double_numeric =
           case_when(
             (respiratory.throat_swab_test_nose_numeric == 1 &
               respiratory.results_antibody_test_numeric == 1) ~ 2,
             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
             respiratory.results_antibody_test_numeric == 1 ~ 1,
             respiratory.results_antibody_test_numeric == 2 ~ 0
           )
         )

dat <- dat %>%
  mutate(covid_test_positive_double =
           recode_factor(
             gad.covid_test_positive_double_numeric,
             `0` = "Negative",
             `1` = "Positive",
             `2` = "Double positive"
           )
         )

>>>>

# Collapsing categories

## Gender
```{r Inspect Gender}
dat.raw %>%
  freq(Gender)

dat.raw %>%
  freq(Gender_numeric)
```

```{r Collapse Gender}
dat.raw <- dat.raw %>%
  mutate(Gender_collapsed_numeric =
           case_when(
             Gender_numeric == 0 ~ 0,
             Gender_numeric == 1 ~ 1,
             Gender_numeric == 2 ~ 2,
             Gender_numeric == 3 ~ 2
           )
         )

dat.raw <- dat.raw %>%
  mutate(Gender_collapsed =
           recode_factor(
             Gender_collapsed_numeric,
             `0` = "Male",
             `1` = "Female",
             `2` = "Non-binary/Self-defined"
           )
         )

dat.raw %>%
  freq(Gender_collapsed)
```

## Ethnicity
```{r Inspect Ethnicity}
dat.raw %>%
  freq(Ethnicity)

dat.raw %>%
  freq(Ethnicity_numeric)
```

```{r Collapse Ethnicity}
dat.raw <- dat.raw %>%
  mutate(Ethnicity_collapsed_numeric =
           case_when(
             Ethnicity_numeric == 1 ~ 0,
             Ethnicity_numeric == 2 ~ 1,
             Ethnicity_numeric == 3 ~ 2,
             Ethnicity_numeric == 4 ~ 3,
             Ethnicity_numeric == 5 ~ 3,
             Ethnicity_numeric == 6 ~ 4
           )
  )

dat.raw <- dat.raw %>%
  mutate(Ethnicity_collapsed =
           recode_factor(
             Ethnicity_collapsed_numeric,
             `0` = "European",
             `1` = "Mixed or multiple ethnic origins",
             `2` = "Asian or Asian British",
             `3` = "African or African British",
             `4` = "Asian or Asian British"
           )
  )

dat.raw %>%
  freq(Ethnicity_collapsed)
```

@@

```{r}
dat %>%
  freq(disorders_total_count)
```

## GAD
```{r}
dat.gad <- dat.raw %>%
  drop_na(
  ) %>%
  filter(
    (data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data")
  )

@@

@@

# COVID
## Recode variable
```{r gad covid test positive double}
dat <- dat %>%
  mutate(covid_test_positive_double_numeric =
           case_when(
             (respiratory.throat_swab_test_nose_numeric == 1 &
               respiratory.results_antibody_test_numeric == 1) ~ 2,
             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
             respiratory.results_antibody_test_numeric == 1 ~ 1,
             respiratory.results_antibody_test_numeric == 2 ~ 0
           )
         )

dat <- dat %>%
  mutate(covid_test_positive_double =
           recode_factor(
             covid_test_positive_double_numeric,
             `0` = "Negative",
             `1` = "Positive",
             `2` = "Double positive"
           )
         )
